\documentclass[letterpaper,10pt]{article}
\usepackage[inline]{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[margin=32pt]{geometry}
\usepackage[none]{hyphenat}
\usepackage{titlesec}
\usepackage[default]{sourcesanspro}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%  suppress the appearance of the section number
\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

\titlespacing*\section{0pt}{0pt}{2pt}
\titlespacing*\subsection{0pt}{6pt}{2pt}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Custom Commands ------------
\newcommand{\resumeItem}[1]{
  \item#1}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{\small{#4}}
    \end{tabular*}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\project}[3]{
    \item{
        \parbox[t]{0.17\textwidth}{\textbf{#1}}
        \parbox[t]{0.82\textwidth}{#2\hfill\small{#3}}}}

\begin{document}
    \section{\huge{Priyavrat Misra}}
    \begin{enumerate*}[label={}, itemjoin={\quad}]
        \item{Hyderabad, India}
        \item{+91XXXXXXXX13}
        \item{\href{https://priyavr.at}{[Website]}}
        \item{\href{mailto:priyavratmisra123@gmail.com}{[Mail]}}
        \item{\href{https://linkedin.com/in/priyavrat-misra}{[LinkedIn]}}
        \item{\href{https://github.com/priyavrat-misra}{[GitHub]}}
    \end{enumerate*}
    \subsection{Summary}
        Software Engineer with a Computer Science background, specializing in writing clean and efficient code. Passionate about accessibility, algorithms, operating systems, and computer architecture, alongside an enthusiasm for blogging and open-source software.
    \subsection{Skills}
    \begin{itemize}[noitemsep, label={}, leftmargin=*]
        \item{
            \textbf{Programming, Query \& Markup Languages} :
            \begin{enumerate*}[label={}, itemjoin={{, }}]
                \item Java
                \item C++
                \item JavaScript
                \item TypeScript
                \item SQL
                \item MongoDB
                \item HTML
                \item CSS
                \item Markdown
            \end{enumerate*}}
        \item{
            \textbf{Frameworks \& Libraries} :
            \begin{enumerate*}[label={}, itemjoin={{, }}]
                \item Spring Boot
                \item JUnit
                \item Angular
                \item RxJS
                \item SLF4J
                \item AssertJ
                \item Apache POI
                \item Jackson
                \item OpenAPI (Swagger)
            \end{enumerate*}}
        \item{
            \textbf{Development Tools} :
            \begin{enumerate*}[label={}, itemjoin={{, }}]
                \item Vim
                \item Git
                \item cURL
                \item GNU Make
                \item Apache Maven
                \item Accessibility Tools (axe DevTools)
                \item Splunk
            \end{enumerate*}}
        \item{
            \textbf{Other Skills} :
            \begin{enumerate*}[label={}, itemjoin={{, }}]
                \item Problem Solving
                \item Unit Testing
                \item Technical Documentation
                \item Web Accessibility (WCAG 2.2)
            \end{enumerate*}}
    \end{itemize}
    \subsection{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {ADP}{Jan 2023 -- Present}
        {Member Technical -- Global Product \& Technology (GPT)}{Hyderabad, Telangana}
        \resumeItemListStart
            \resumeItem{Took individual ownership to enhance ADP SmartCompliance for parallel onboarding with ADP HCM systems (Workforce Now, Lyric, Vantage, TotalSource, GlobalView, and Enterprise). Implemented efficient, asynchronous event handler webhooks and APIs to streamline data exchange, automate client information population, and substantially reduce onboarding time.}
            \resumeItem{Contributed significantly in streamlining the migration process of 76,850 ADP Workforce Now clients from Wage Garnishment Processing Service to Full-Service Wage Garnishment, reducing migration time from 12–16 weeks to under 2 weeks and generating \$20M in revenue.}
            \resumeItem{Enabled seamless onboarding of Oracle Fusion Cloud HCM clients to ADP SmartCompliance Employment Verification services by securely capturing client data and credentials for HCM integration.}
            \resumeItem{Developed intuitive and responsive user interfaces for ADP SmartCompliance, prioritizing accessibility and usability.}
        \resumeItemListEnd
        \resumeSubheading
        {Indian Institute of Science Education and Research}{Feb 2020 -- Mar 2020}
        {Intern}{Brahmapur, Odisha}
        \resumeItemListStart
            \resumeItem{Enhanced the user interface of iiserbpr.ac.in, improving usability and visual design for a seamless experience.}
            \resumeItem{Collaborated with senior engineers and participated in educational sessions, gaining hands-on experience with industry-standard tools and technologies.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \subsection{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Parala Maharaja Engineering College}{Aug 2017 -- Jul 2021}
        {Bachelor of Technology in Computer Science and Engineering}{Brahmapur, Odisha}
        \resumeItemListStart
            \resumeItem{
                \textbf{Relevant Coursework} :
                \begin{enumerate*}[label={}, itemjoin={{, }}]
                    \item Data Structures and Algorithms
                    \item Discrete Mathematics
                    \item Operating Systems
                    \item Computer Networks
                    \item Databases
                    \item Computer Organization and Architecture
                \end{enumerate*}}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \subsection{Projects}
    \begin{itemize}[noitemsep, label={}, leftmargin=*]
        \project
        {https://priyavr.at}
        {Personal website and blogging platform built with Hugo.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://priyavr.at}{[Site]}}
                \item{\href{https://github.com/priyavrat-misra/personal-website}{[Code]}}
            \end{enumerate*}
        }
        \project
        {poijo}
        {Java library with a fluent, annotation-driven API for working with Excel spreadsheets.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://github.com/priyavrat-misra/poijo}{[Code]}}
            \end{enumerate*}
        }
        \project
        {mish}
        {Lightweight Linux shell implemented in C with basic command execution.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://asciinema.org/a/702244}{[Demo]}}
                \item{\href{https://github.com/priyavrat-misra/mish}{[Code]}}
            \end{enumerate*}
        }
        \project
        {amaze}
        {Visually appealing maze generator built with C++ and SFML.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://github.com/priyavrat-misra/amaze}{[Code]}}
            \end{enumerate*}
        }
        \project
        {computime}
        {Telegram bot that estimates YouTube video duration at custom playback speeds.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://telegram.me/iamspeed_bot}{[Demo]}}
                \item{\href{https://github.com/priyavrat-misra/computime}{[Code]}}
            \end{enumerate*}
        }
    	\project
    	{xrays-and-gradcam}
    	{CNN based X-ray classifier for COVID-19 and other inflammatory lung diseases.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://doi.org/10.1007/s11042-023-16084-4}{[Paper]}}
                \item{\href{https://github.com/priyavrat-misra/xrays-and-gradcam}{[Code]}}
            \end{enumerate*}
        }
        \project
        {image-colorizer}
        {Convolutional Autoencoder model with residual networks to colorize grayscale images.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://github.com/priyavrat-misra/image-colorizer}{[Code]}}
            \end{enumerate*}
        }
        \project
        {scifi-lorem}
        {Character-level RNN for generating synthetic science fiction text samples.}
        {
            \begin{enumerate*}[label={}, itemjoin={\quad}]
                \item{\href{https://github.com/priyavrat-misra/scifi-lorem}{[Code]}}
            \end{enumerate*}
        }
    \end{itemize}
    \subsection{Awards \& Activities}
    \begin{itemize}[noitemsep, leftmargin=*]
        \item{Secured third place by cycling 105 KM in \textit{\#ADPIndiaTurns25} challenge ride (2024).}
        \item{Winner, ADP Global Product and Technology (GPT) Connect Artwork Competition (2023).}
        \item{Winner, ADP SmartCompliance Solutions Best Ad Experience Contest (2023).}
        \item{Recipient, Udacity Deep Learning Nanodegree Scholarship (2020), awarded to top 5\% performers among 15,000 participants.}
        \item{Gold Medalist, Quiz organized by Inspire Science Camp, Department of Science and Technology, Government of India (2016).}
        \item{Silver Medalist, National Science Olympiad 2014-15, School-level.}
        \item{Gold Medalist, National Science Olympiad 2013-14, School-level and City-level.}
    \end{itemize}
\end{document}
